---
title: "Day6"
output: github_document
date: 2018-11-19
---

```{r message=FALSE}
library(tidyverse)
library(knitr)
```


# More dental care

```{r message=FALSE, warning=FALSE}
# Load data
dental_data <- read_csv2("../Class_files/Statistikdatabasen_2018-01-23 14_46_26.csv", skip = 1, n_max = 580)
pop_data <- read_csv("BE0101A5.csv", skip = 2)
```

```{r}
dental_data_tidy <- gather(dental_data, `2010`:`2016`, key = "År", value = "Antal") %>%
  unite(id, Region, Kön, År, remove = FALSE) %>%
  mutate(id = tolower(id))

pop_data_tidy <- gather(pop_data, `2006`:`2016`, key = "år", value = "antal") %>%
  separate(region, c("nr", "namn1", "namn2")) %>%
  replace_na(list(namn2 = "")) %>%
  unite(region, namn1, namn2, sep = "") %>%
  unite(id, region, kön, år, remove = FALSE) %>%
  mutate(id = tolower(id))

left_join(dental_data_tidy, pop_data_tidy, by = "id")
```


# Sytembolaget

We will know look at changes to Sytembolaget's assortment. We start by loading data and create dataframes for new beverages and beverages that have been removed from the assortment.

```{r warning=FALSE, message=FALSE}
# Load data 
sortiment_11_19 <- read_csv("systembolaget2018-11-19.csv")
sortiment_10_08 <- read_csv("../Class_files/systembolaget2018-10-08.csv")

# Dataframe of newly added beverages
sortiment_nytt <- setdiff(sortiment_11_19, sortiment_10_08)

# Dataframe newly removed beverages
sortiment_borta <- setdiff(sortiment_10_08, sortiment_11_19)
```

Now that we have created dataframes. Let us look at what types of beverages have been removed and what have been added.

```{r}
# List 5 categories with most added beverages
new_table <- sortiment_nytt %>% 
  group_by(Varugrupp) %>%
  summarize(num_added = n()) %>%
  arrange(desc(num_added), Varugrupp) %>%
  select(Varugrupp, num_added) %>%
  head(5) %>% 
  kable(col.names = c("Varugrupp", "Beverages added"))

# List 5 categories with most removed beverages
removed_table <- sortiment_borta %>%
  group_by(Varugrupp) %>%
  summarize(num_removed = n()) %>%
  arrange(desc(num_removed), Varugrupp) %>%
  select(Varugrupp, num_removed) %>%
  head(5) %>% 
  kable(col.names = c("Varugrupp", "Beverages removed"))
```

### Five categories with most new beverages

`r new_table`


### Five categories with most removed beverages

`r removed_table`

We can see that it appears that the removed beverages mostly have been replaced by new beverages in the same categories. We could create a graph to show the net difference within each category but for now we will move on.

# Pokémon

```{r message=FALSE}
# Load pokémon data
pokemon <- read_csv("https://raw.githubusercontent.com/veekun/pokedex/master/pokedex/data/csv/pokemon.csv")
types <- read_csv("https://raw.githubusercontent.com/veekun/pokedex/master/pokedex/data/csv/types.csv")
pokemon_types <- read_csv("https://raw.githubusercontent.com/veekun/pokedex/master/pokedex/data/csv/pokemon_types.csv")
```

```{r}
# Join and spread data
pokemon_types_identifier <- left_join(pokemon_types, types, by = c("type_id" = "id")) %>%
  select(pokemon_id, slot, identifier) %>%
  spread(slot, identifier)

# Rename columns
colnames(pokemon_types_identifier)[2:3] <- c("slot1", "slot2")

# Join to final dataframe
left_join(pokemon_types_identifier, pokemon, by = c("pokemon_id" = "id")) %>%
  select(pokemon_id, identifier, slot1, slot2 , weight, height) %>%
  head()
```


# More birdwatching

