---
title: "Day7"
output: github_document
---

```{r message=FALSE, warning=FALSE}
library(DBI)
library(tidyverse)
```


# SL SQL

Let us start by connecting to sthlm_metro database.

```{r}
con <- dbConnect(RSQLite::SQLite(), "../Class_files/sthlm_metro.sqlite")
dbListTables(con)
```

We that the database contains three different tables. To answer the question how they relate to eachother, let us load some rows from each.

```{r}
dbGetQuery(con, "SELECT * FROM Line LIMIT 3")   # Line table
dbGetQuery(con, "SELECT * FROM LinePlatform LIMIT 3")   # LinePlatform table
dbGetQuery(con, "SELECT * FROM Platform LIMIT 3")   # Platform table
```

We can know see how they connect to eachother:

- ```Line``` connects to ```LinePlatform``` through ```LineNumber```.
- ```Platform``` connects to ```LinePlatform``` through ```PlatformNumber```.
- ```Line``` does not connect to ```Platform```.

**The first task is to query for the LineName from table Line where LineNumber is 18.**

```{r}
line_name_18 <- dbGetQuery(con, "SELECT LineName FROM Line WHERE LineNumber = 18") %>%
  pull()
```

The line name of line number 18 is *"`r line_name_18`"*. Let us move on to the next task.

**Query for the number of stops on LineNumber 18 Direction 1.**

```{r}
count_stops <- dbGetQuery(con, "SELECT COUNT(PlatformNumber) FROM LinePlatform WHERE LineNumber = 18 AND Direction = 1") %>%
  pull()
```

Line number 18 has *`r count_stops`* stops in direction 1.

**Query for the five most southern StationName, where position is measured as the average Latitude of its PlatformNumber.**

```{r}
southern_stations <- dbGetQuery(con, "SELECT StationName, AVG(Latitude) as avgLatitude 
                                FROM Platform 
                                GROUP BY StationName 
                                ORDER BY avgLatitude
                                LIMIT 5")

knitr::kable(southern_stations, col.names = c("Station", "Latitude"))
```

The stations that we are given look reasonable. At least they are all south of Stockholm.

**Query for all StationName on LineNumber 18 Direction 1.**

```{r}
dbGetQuery(con, "SELECT DISTINCT(StationName)
           FROM Platform 
           LEFT JOIN LinePlatform ON Platform.PlatformNumber = LinePlatform.PlatformNumber
           WHERE LineNumber = 18 AND Direction = 1
           ORDER BY StationName")
```

End by disconnect from database.

```{r}
dbDisconnect(con)
```

